Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
emphasize importance of separate initialization in ECOC example
XXX @mblondel, I'm not really familiar with this algorithm;
maybe it's easier to use an OvR naive Bayes instead?

As an example, a logistic regression classifier
uses by default a one-vs.-rest scheme
for performing multiclass classification.
If multiclass classification based on error-correcting codes
\citep{dietterich1995solving} is desired instead,
then this can achieved  using an \texttt{OutputCodeClassifier} meta-estimator
wrapping a \texttt{LogisticRegression} estimator:
\begin{pythoncode}
from sklearn.linear_model import LogisticRegression
from sklearn.multiclass import OutputCodeClassifier

ecoc_lr = OutputCodeClassifier(LogisticRegression(penalty="l1"))
\end{pythoncode}

>>>>

As an example, a logistic regression classifier
uses by default a one-vs.-rest scheme
for performing multiclass classification.
If multiclass classification based on error-correcting codes
is desired instead,
then this can achieved  using an \texttt{OutputCodeClassifier} meta-estimator
wrapping a \texttt{LogisticRegression} estimator:
\begin{pythoncode}
from sklearn.linear_model import LogisticRegression
from sklearn.multiclass import OutputCodeClassifier

ecoc_lr = OutputCodeClassifier(LogisticRegression(penalty="l1"))
\end{pythoncode}
The \texttt{OutputCodeClassifier} object
\textit{clones} the LR estimator multiple times for learning,
resulting in a set of estimator objects with the same settings
that each perform a binary classification
(see \citealt{dietterich1995solving} for the algorithm).
The snippet thus exemplifies the importance
of separating object instantiation and actual learning.
